\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-19 notes/2loopNLSM.tex
Small edits

Aside from a few special theories that permit an off-shell Lagrangian description \citepls{}, color-dual integrands are constructed from an ansatz. The four conditions we impose on an ansatz are summarized here and elaborated on below.\footnote{The four ansatz conditions are similar to those of Ref.~\cite{Bern:2015ooa} except that the authors demand that the numerators have the same loop power counting as Feynman gauge Feynman rules.  This is an additional assumption that is most emphatically not made here.}
\begin{enumerate}
\item \textbf{Off-shell Locality}: Diagram numerators are polynomials in momenta and
  polarizations, \eg the diagrams only have poles given by the
  propagators of the diagrams.
  \item  \textbf{Color-kinematics duality}: The numerators obey the same Jacobi identities as the color factors.
This implicitly requires that the integrand is expressed in terms of purely cubic diagrams.
\item  \textbf{Graph symmetries}: The diagram numerators are only a function of the diagram's topology and labeling.  Furthermore, the diagram numerators are invariant under the automorphisms of the diagrams \emph{including signs that compensate for color-factor sign changes}.
\item  \textbf{On-shell Unitarity }: The cuts of the ansatz must reproduce the physical unitarity cuts of the theory when internal momenta are taken on-shell.
\end{enumerate}

@@

@@

Proceeding to the next-to-maximal cuts, we continue to avoid
pathological diagrams including the newly-appearing type discussed in
\cref{eq:other-path}.
After discarding these types of cuts, there are 8 cut topologies (see \cref{fig:ym-nmc}) ignoring cuts with dangling trees.
Seven of these next-to-maximal cuts are consistent with the kinematic Jacobi
relations and symmetries.  Interestingly, the ``kissing triangles'' or ``bowtie''
cut,
\begin{equation*}
   \NMCutC \,,
\end{equation*}
cannot be satisfied by either the unrestricted or the BDN-restricted
ansatz with Jacobi relations and symmetries applied. \jm{I would just focus on what we do since we do something more general than BDN.}
\begin{figure}
\centering
 { \NMCutH, \NMCutG,  \NMCutD,\NMCutB, 
 \\
 \NMCutE, \NMCutF, \NMCutA, \NMCutC,  }
  \caption{The 8 non-pathological next-to-maximal-cut diagrams.}
  \label{fig:ym-nmc}
\end{figure}

@@

\jm{I am intentionally shying away from really firm statements like 'you must abandon locality' because there are always loopholes and we made a lot of other assumptions in fixing our \ansatze{}.}

>>>>

Aside from a few special theories that permit an off-shell Lagrangian description \cite{Monteiro2011pc, Cheung:2016prv, Cheung:2021zvb, Cheung:2020djz, Ben-Shahar:2022ixa, Ben-Shahar:2021zww, Ben-Shahar:2021doh}, color-dual integrands are constructed from an ansatz.
The four conditions we impose on an ansatz are summarized here and elaborated on below.\footnote{The four ansatz conditions are similar to those of Ref.~\cite{Bern:2015ooa} except that the authors demand that the numerators have the same loop power counting as Feynman gauge Feynman rules.  This is an additional assumption that is most emphatically not made here.}
\begin{enumerate}
\item \textbf{Off-shell Locality}: Diagram numerators are polynomials in momenta and
  polarizations, \eg the diagrams only have poles given by the
  propagators of the diagrams.
  \item  \textbf{Color-kinematics duality}: The numerators obey the same Jacobi identities as the color factors.
This implicitly requires that the integrand is expressed in terms of purely cubic diagrams.
\item  \textbf{Graph symmetries}: The diagram numerators are only a function of the diagram's topology and labeling.  Furthermore, the diagram numerators are invariant under the automorphisms of the diagrams \emph{including signs that compensate for color-factor sign changes}.
\item  \textbf{On-shell Unitarity }: The cuts of the ansatz must reproduce the physical unitarity cuts of the theory when internal momenta are taken on-shell.
\end{enumerate}

@@

\jm{Rather than quoting the number of parameters in the BDN ansatz, I would prefer to just focus on what we did since it's more general.  I don't want it to sound like we just patched a minor hole in their argument when I think you've done something much cooler by pinpointing the failure to the bowtie graph.}

@@

Proceeding to the next-to-maximal cuts, we continue to avoid
pathological diagrams including the newly-appearing type discussed in
\cref{eq:other-path}.
After discarding these types of cuts, there are 8 cut topologies (see \cref{fig:ym-nmc}) ignoring cuts with dangling trees.
Seven of these next-to-maximal cuts are consistent with the kinematic Jacobi
relations and symmetries.  Interestingly, the ``kissing triangles'' or ``bowtie''
cut,
\begin{equation*}
   \NMCutC \,,
\end{equation*}
cannot be satisfied by either the unrestricted or the BDN-restricted
ansatz with Jacobi relations and symmetries applied. 
\begin{figure}
\centering
 { \NMCutH, \NMCutG,  \NMCutD,\NMCutB, 
 \\
 \NMCutE, \NMCutF, \NMCutA, \NMCutC,  }
  \caption{The 8 non-pathological next-to-maximal-cut diagrams.}
  \label{fig:ym-nmc}
\end{figure}

@@

\jm{I am intentionally shying away from really firm statements like `you must abandon locality' because there are always loopholes and we made a lot of other assumptions in fixing our \ansatze{}.}
